Floral resource choice by bumble bee species in the Berchtesgadener Alps

### 2020-12-03 analyses/niche_relations_v6B.Rmd
realized mistake about not standardizing by site-date

# Prepare workspace
## Load packages 
```{r message=FALSE, warning=FALSE, include=FALSE, echo = FALSE}
library(bipartite)
library(mgcv)
library(mgcViz)
library(vegan)
library(ggvegan)
library(ggrepel)
library(treemapify)
#library(RColorBrewer)
library(tidyverse)
library(lubridate)
library(patchwork)
library(tidymodels)
```

@@

# Network
net <- read_csv("../processed_data/network.csv") %>%
  mutate(year = factor(year)) %>% # convert year to factor
  left_join(site_data, by = "site") %>% # add site data
  ungroup() %>%
  arrange(site, date) %>%
  left_join(fl_traits) %>% # add floral traits
  group_by(site) %>%
  mutate(period = cut_interval(dayofyear, 4, labels = c("early", "mid1", "mid2", "late"))) # divide each elev.class2 into 4 equal time slices

@@

We will parse the samples by elevation class and season, dividing the samples from each site into equal-interval quarters
```{r}
samples <- net %>%
  filter(bb.sp %in% c("bss", "pasc", "prat", "hort", "soro", "wurf")) %>% # focal species
  #group_by(elev.class2) %>%
  group_by(site) %>%
  mutate(period = cut_interval(dayofyear, 4, labels = c("early", "mid1", "mid2", "late"))) %>%
  group_by(site, period, dayofyear) %>%
  summarize(obs = n()) %>%
  left_join(site_data) %>%
  mutate(date = as_date(dayofyear))

@@

  scores <- y %>% 
    filter(Score != "T.len") %>%
    filter((abs(MDS1) > 0.25 | abs(MDS2) > 0.25) | Score == "BB.sp")

@@

# Fortify envfit() object fitted to BB tongue length data
envfit_fort <- function(x){
  fortify(x) %>%
  select(Score = Type, Label, MDS1, MDS2) %>%
  mutate(Label = case_when(Label == "pbl.w" ~ "T.len"),
         Score = case_when(Score == "Vector" ~ "T.len"))
}

# Fortify PCOA and add the results of an envfit() to BB tongue length
pcoa_fort <- function(x, y){
  fortify(x, axes = 1:2) %>%
  bind_rows(y) %>%
  mutate(Score = case_when(
    Score == "species" ~ "FL.sp",
    Score == "sites" ~ "BB.sp",
    Score == "T.len" ~ "T.len"))
}

# Plot PCoA ordination with arrow for tongue length envfit()
pcoa_plot <- function(x, y, min_score = 0.25) {
  ggplot(filter(x, (abs(MDS1) > min_score | abs(MDS2) > min_score) | (Score %in% c("BB.sp", "T.len")))) + # to avoid overplotting, we can filter to include only floral species > loading threshold
    geom_point(aes(MDS1, MDS2, color = Score)) +
    geom_text_repel(aes(MDS1, MDS2, color = Score, label = Label), key_glyph = "rect") +
    geom_segment(data = y, 
               aes(x = 0, y = 0, xend = MDS1, yend = MDS2, colour = Label),
               arrow = arrow(), size = 2, alpha = 0.5, key_glyph = "rect") +
    theme_light() +
    coord_fixed() # Gavin Simpson says this is **really** important
}

# Generates PCoAs, ADONIS tests, and ordination plots (fully aggregated)
## The ... represents the variables we will use to parse our analysis. For aggregate analysis, just leave the ...
## unpopulated, e.g. niche_analysis(net, bb_traits, plant.sp). 
## To parse by elev.class2: niche_analysis(net, bb_traits, plant.sp)
## To parse by  elev.class2, period, and pollen: niche_analysis(net, bb_traits, plant.sp, period, pollen)
## You get the idea. You should anyway -- you wrote it. https://tidyeval.tidyverse.org/multiple.html
niche_analysis <- function(x, y, criterion, ...) {

@@

  x %>%
    filter(caste != "male") %>%
    filter(!bb.sp %in% c("psit", "gers", "humi")) %>% # omit parasitic species, gers because it's a specialist, humi because it's so rare
    group_by(..., bb.sp, !!criterion) %>% # pooling all sites and years
    summarize(freq = n()) %>% # get interaction frequency for each BB-FL pair
    group_by(..., bb.sp) %>%
    mutate(prop = freq/sum(freq)) %>% # get proportional interaction frequency for each BB-FL pair
    dplyr::select(-freq) %>% # drop freq variable
    group_by(...) %>%
    nest() %>% # nest into list-column
    mutate(comm1 = map(data, # spread into the kind of array vegan likes
                       function(x) pivot_wider(x, names_from = !!criterion, values_from = prop) %>%
                         replace(is.na(.), 0)
                       ), 
           comm2 = map(comm1, # column to rowname
                       function(x) column_to_rownames(x, var = "bb.sp")
                       ),
           pcoa = map(comm2, # call PCoA
                      function(x) capscale(x ~ 1, distance = "horn")
                      ),
           traits = map(comm1, # join BB traits
                        function(x) x %>% 
                          left_join(y) %>% # y is the trait table, an argument in the main function call
                          column_to_rownames(var = "bb.sp") %>% 
                          select(pbl.w) # pbl.w is the variable I'm interested in
                        ),
           adonis = map2(comm2, traits, # run adonis permuatation test for distance ~ tongue class
                         function(x, y) adonis(x ~ pbl.w, data = y, method = "horn")
                         ),
           envfit = map2(pcoa, traits, function(x, y) envfit(x, y)),
           envfit.fort = map(envfit, envfit_fort),
           pcoa.fort = map2(pcoa, envfit.fort, pcoa_fort),
           pcoa.plot = map2(pcoa.fort, envfit.fort, pcoa_plot), 
           envfit.r2 = map(envfit, function(x) x$vectors$r),
           envfit.p = map(envfit, function(x) x$vectors$pvals),
           adonis.r2 = map(adonis, # extract adonis r2
                           function(x) x$aov.tab$R2[[1]]
                           ),
           adonis.p = map(adonis, # extract adonis p-value
                          function(x) x$aov.tab$'Pr(>F)'[[1]]
                          ),
           ordisurf = map2(pcoa, traits, function(x, y) ordisurf(x ~ pbl.w, data = y, k = 8)),
           ordisurf.dev_exp = map(ordisurf, function(x) summary(x)$dev.expl),
           ordisurf.p = map(ordisurf, function(x) summary(x)$s.pv),
           ordisurf.plot = map2(ordisurf, pcoa.fort, surfplot),
           MDS1 = map(pcoa, # extract variance explained by MDS1
                      function(x) x$CA$eig[[1]] / sum(x$CA$eig)
                      ), 
           MDS2 = map(pcoa, # extract variance explained by MDS2
                      function(x) x$CA$eig[[2]] / sum(x$CA$eig)
                      )) %>%
    unnest(cols = c(ordisurf.dev_exp, ordisurf.p, envfit.r2, envfit.p, adonis.r2, adonis.p, MDS1, MDS2)) %>% # these are lists of length = 1, so unnesting them simply displays the value
    select(..., comm2, traits, pcoa, ordisurf, ordisurf.dev_exp, ordisurf.p, ordisurf.plot, envfit, envfit.fort, pcoa.fort, pcoa.plot, envfit.r2, envfit.p, adonis.r2, adonis.p, MDS1, MDS2)
}

@@

  a <- x %>%
    filter(caste != "male") %>%
    filter(bb.sp %in% c("bss", "pasc", "prat", "hort", "soro", "wurf")) %>% # focal species
    left_join(y) %>%
    #group_by(elev.class2) %>%
    group_by(site) %>%
    mutate(period = cut_interval(dayofyear, 4, labels = c("early", "mid1", "mid2", "late"))) %>%
    group_by(site, period, pbl.fac, !!criterion) %>% # group by site, date, bee species, plant species
    summarize(freq = n()) %>% # calculate interaction frequency per species pair within each site
    unite(webID, c(site, period), sep = "_") %>%
    ungroup() %>%
    dplyr::select(higher = pbl.fac, lower = !!criterion, webID, freq) %>% # rename columns to match bipartite's expectations
    data.frame() %>% # convert to data frame
    frame2webs() %>% # convert to to bipartite web
    map(specieslevel, level = "higher", index = indices) %>%
    map(rownames_to_column) %>%
    map(as_tibble) %>%
    bind_rows(.id = "webID") %>% # Collapse list into big data frame
    rename(pbl.fac = rowname) %>%
    separate(webID, c("site", "period"), sep =  "_") %>%
    left_join(z) %>%
    filter(pbl.fac %in% c("long", "short")) %>% # for some reason, a few rows have a "1" for pbl.fac, and I don't know where this comes from; this gets rid of it, but I would still like to know why
    mutate(site = factor(site),
           period = factor(period, levels = c("early", "mid", "late")))

  b <- x %>%
    filter(caste != "male") %>%
    filter(bb.sp %in% c("bss", "pasc", "prat", "hort", "soro", "wurf")) %>% # focal species
    #group_by(elev.class2) %>%
    group_by(site) %>%
    mutate(period = cut_interval(dayofyear, 4, labels = c("early", "mid1", "mid2", "late"))) %>%
    left_join(bb_traits) %>%
    group_by(site, period, pbl.fac) %>% # group by site, date, bee species, plant species
    summarize(abund = n()) %>%
    group_by(site, period) %>%
    mutate(prop = abund/sum(abund))

@@

  a <- x %>%
    filter(caste != "male") %>%
    filter(bb.sp %in% c("bss", "pasc", "prat", "hort", "soro", "wurf")) %>% # focal species
    left_join(y) %>%
    # group_by(elev.class2) %>%
    # mutate(period = cut_interval(dayofyear, 4, labels = c("early", "mid1", "mid2", "late"))) %>%
    #group_by(site, period, pbl.fac, !!criterion) %>% # group by site, date, bee species, plant species
    group_by(site, pbl.fac, !!criterion) %>% # group by site, date, bee species, plant species
    summarize(freq = n()) %>% # calculate interaction frequency per species pair within each site
    #unite(webID, c(site, period), sep = "_") %>%
    ungroup() %>%
    #dplyr::select(higher = pbl.fac, lower = !!criterion, webID, freq) %>% # rename columns to match bipartite's expectations
    dplyr::select(higher = pbl.fac, lower = !!criterion, webID = site, freq) %>% # rename columns to match bipartite's expectations
    data.frame() %>% # convert to data frame
    frame2webs() %>% # convert to to bipartite web
    map(specieslevel, level = "higher", index = indices) %>%
    map(rownames_to_column) %>%
    map(as_tibble) %>%
    bind_rows(.id = "webID") %>% # Collapse list into big data frame
    #rename(pbl.fac = rowname) %>%
    rename(pbl.fac = rowname,
           site = webID) %>%
    #separate(webID, c("site", "period"), sep =  "_") %>%
    left_join(z) %>%
    filter(pbl.fac %in% c("long", "short")) %>% # for some reason, a few rows have a "1" for pbl.fac, and I don't know where this comes from; this gets rid of it, but I would still like to know why
    # mutate(site = factor(site),
    #        period = factor(period, levels = c("early", "mid", "late")))
    mutate(site = factor(site))

  b <- x %>%
    filter(caste != "male") %>%
    filter(bb.sp %in% c("bss", "pasc", "prat", "hort", "soro", "wurf")) %>% # focal species
    # group_by(elev.class2) %>%
    # mutate(period = cut_interval(dayofyear, 4, labels = c("early", "mid1", "mid2", "late"))) %>%
    left_join(bb_traits) %>%
   # group_by(site, period, pbl.fac) %>% # group by site, date, bee species, plant species
    group_by(site, pbl.fac) %>% # group by site, date, bee species, plant species
    summarize(abund = n()) %>%
    #group_by(site, period) %>%
    group_by(site) %>%
    mutate(prop = abund/sum(abund))

@@

## 1.1 Ordination by species with post-hoc fitting of tongue length  
### Script
```{r message=FALSE, warning=FALSE, echo = FALSE}
# By plant.sp
niche.tax <- niche_analysis(net, bb_traits, criterion = plant.sp.abb)
niche.tax.plot <- niche.tax$pcoa.plot[[1]]
niche.tax.surfplot <- niche.tax$ordisurf.plot
nich.tax.baseplot <- plot(niche.tax$ordisurf[[1]])
niche.tax$ordisurf.plot
plot(niche.tax$ordisurf[[1]])

# By ktype
niche.morph <- niche_analysis(net, bb_traits, criterion = k.type.s)
niche.morph.plot <- niche.morph$pcoa.plot[[1]]

## Taxonomic and morphological together
pdf("../analyses/output/niche_pcoa.pdf", height = 8.5, width = 11)
(niche.tax.plot + ggtitle("Taxonomic") | niche.morph.plot + ggtitle("Morphological")) + plot_layout(guides = 'collect') 
dev.off()

@@

## Extract and name plots
niche_high.tax.plot <- filter(niche_x_elev.tax, elev.class2 == "high")$pcoa.plot[[1]] + ggtitle("high/Tax")
niche_mid.tax.plot <- filter(niche_x_elev.tax, elev.class2 == "mid")$pcoa.plot[[1]] + ggtitle("mid/Tax")
niche_low.tax.plot <- filter(niche_x_elev.tax, elev.class2 == "low")$pcoa.plot[[1]] + ggtitle("low/Tax")

# Morphological
niche_x_elev.morph <- niche_analysis(net, bb_traits, criterion = k.type.s, elev.class2)

## Extract and name plots
niche_high.morph.plot <- filter(niche_x_elev.morph, elev.class2 == "high")$pcoa.plot[[1]] + ggtitle("high/morph")
niche_mid.morph.plot <- filter(niche_x_elev.morph, elev.class2 == "mid")$pcoa.plot[[1]] + ggtitle("mid/morph")
niche_low.morph.plot <- filter(niche_x_elev.morph, elev.class2 == "low")$pcoa.plot[[1]] + ggtitle("low/morph")

## Display plots on grid
pdf("../analyses/output/niche_x_elev_pcoa.pdf", height = 8.5, width = 11)
(niche_high.tax.plot | niche_high.morph.plot) /
(niche_mid.tax.plot | niche_mid.morph.plot) /
(niche_low.tax.plot | niche_low.morph.plot) + plot_layout(guides = 'collect') 
dev.off()
```

@@

## Extract and name plots
niche_high_early.tax.plot <- filter(niche_x_elevperiod.tax, elev.class2 == "high" & period == "early")$pcoa.plot[[1]] 
niche_high_mid1.tax.plot <- filter(niche_x_elevperiod.tax, elev.class2 == "high" & period == "mid1")$pcoa.plot[[1]] 
niche_high_mid2.tax.plot <- filter(niche_x_elevperiod.tax, elev.class2 == "high" & period == "mid2")$pcoa.plot[[1]] 
niche_high_late.tax.plot <- filter(niche_x_elevperiod.tax, elev.class2 == "high" & period == "late")$pcoa.plot[[1]]

niche_mid_early.tax.plot <- filter(niche_x_elevperiod.tax, elev.class2 == "mid" & period == "early")$pcoa.plot[[1]]
niche_mid_mid1.tax.plot <- filter(niche_x_elevperiod.tax, elev.class2 == "mid" & period == "mid1")$pcoa.plot[[1]] 
niche_mid_mid2.tax.plot <- filter(niche_x_elevperiod.tax, elev.class2 == "mid" & period == "mid2")$pcoa.plot[[1]]
niche_mid_late.tax.plot <- filter(niche_x_elevperiod.tax, elev.class2 == "mid" & period == "late")$pcoa.plot[[1]]

niche_low_early.tax.plot <- filter(niche_x_elevperiod.tax, elev.class2 == "low" & period == "early")$pcoa.plot[[1]]
niche_low_mid1.tax.plot <- filter(niche_x_elevperiod.tax, elev.class2 == "low" & period == "mid1")$pcoa.plot[[1]]
niche_low_mid2.tax.plot <- filter(niche_x_elevperiod.tax, elev.class2 == "low" & period == "mid2")$pcoa.plot[[1]]
niche_low_late.tax.plot <- filter(niche_x_elevperiod.tax, elev.class2 == "low" & period == "late")$pcoa.plot[[1]]

@@

## Extract and name plots
niche_high_early.morph.plot <- filter(niche_x_elevperiod.morph, elev.class2 == "high" & period == "early")$pcoa.plot[[1]]
niche_high_mid1.morph.plot <- filter(niche_x_elevperiod.morph, elev.class2 == "high" & period == "mid1")$pcoa.plot[[1]] 
niche_high_mid2.morph.plot <- filter(niche_x_elevperiod.morph, elev.class2 == "high" & period == "mid2")$pcoa.plot[[1]] 
niche_high_late.morph.plot <- filter(niche_x_elevperiod.morph, elev.class2 == "high" & period == "late")$pcoa.plot[[1]]

niche_mid_early.morph.plot <- filter(niche_x_elevperiod.morph, elev.class2 == "mid" & period == "early")$pcoa.plot[[1]]
niche_mid_mid1.morph.plot <- filter(niche_x_elevperiod.morph, elev.class2 == "mid" & period == "mid1")$pcoa.plot[[1]]
niche_mid_mid2.morph.plot <- filter(niche_x_elevperiod.morph, elev.class2 == "mid" & period == "mid2")$pcoa.plot[[1]] 
niche_mid_late.morph.plot <- filter(niche_x_elevperiod.morph, elev.class2 == "mid" & period == "late")$pcoa.plot[[1]]

>>>>

# Prepare workspace
## Load packages 
```{r message=FALSE, warning=FALSE, include=FALSE, echo = FALSE}
library(bipartite)
library(mgcv)
library(mgcViz)
library(vegan)
library(ggvegan)
library(ggrepel)
library(treemapify)
library(tidyverse)
library(lubridate)
library(patchwork)
library(tidymodels)
```

@@

# Network
net <- read_csv("../processed_data/network.csv") %>%
  mutate(year = factor(year)) %>% # convert year to factor
  left_join(site_data, by = "site") %>% # add site data
  ungroup() %>%
  arrange(site, date) %>%
  left_join(fl_traits) %>% # add floral traits
  group_by(site) %>%
  mutate(period = cut_interval(dayofyear, 3, labels = c("early",  "mid", "late"))) # divide each elev.class2 into 4 equal time slices

@@

We will parse the samples by elevation class and season, dividing the samples from each site into equal-interval quarters
```{r}
samples <- net %>%
  filter(bb.sp %in% c("bss", "pasc", "prat", "hort", "soro", "wurf")) %>% # focal species
  #group_by(elev.class2) %>%
  group_by(site) %>%
  mutate(period = cut_interval(dayofyear, 3, labels = c("early",  "mid", "late"))) %>%
  group_by(site, period, dayofyear) %>%
  summarize(obs = n()) %>%
  left_join(site_data) %>%
  mutate(date = as_date(dayofyear))

@@

  scores <- y %>% 
    #filter((abs(MDS1) > 0.25 | abs(MDS2) > 0.25) | Score == "BB.sp")
    filter((abs(MDS1) > 0.1 | abs(MDS2) > 0.1) | Score == "BB.sp")

@@

# Fortify PCOA and add the results of an envfit() to BB tongue length
pcoa_fort <- function(x){
  fortify(x, axes = 1:2) %>%
  mutate(Score = case_when(
    Score == "species" ~ "FL.sp",
    Score == "sites" ~ "BB.sp"))
}

# Plot PCoA; to avoid overplotting, scores < min_score are not plotted
pcoa_plot <- function(x, min_score = 0.25) {

  # # Add T.class variable for the BB.sp subset of the PCoA
  # t.class <- x %>%
  #   filter(Score == "BB sp.") %>%
  #   mutate(T.class = factor(if_else(
  #     Label %in% c("hort", "pasc", "wurf", "gers", "mend", "hypn"), "long", "short"))
  #     )

  # ggplot(filter(x, (abs(MDS1) > min_score | abs(MDS2) > min_score) | (Score == "BB.sp")), 
  #        aes(MDS1, MDS2, color = Score)) + # no threshold for BB spp
  ggplot(x, aes(MDS1, MDS2, color = Score)) +
    #geom_polygon(data = t.class, aes(MDS1, MDS2, linetype = T.class), # draw polygons around T classes
     #            color = "gray70", fill = NA, size = 1.25, key_glyph = "abline") +
    geom_point(size = 2, alpha = 0.75) + # add points
    ggrepel::geom_text_repel(aes(label = Label), key_glyph = "rect", size = 3) + # add labels
    coord_fixed() + # Gavin Simpson says this is **really** important
    theme_classic() +
    theme(legend.title=element_blank())
}

# Generates PCoAs, ordisurfs, ADONIS tests, and ordination plots 
## The ... represents the variables we will use to parse our analysis. For aggregate analysis, just leave the ...
## unpopulated, e.g. niche_analysis(net, bb_traits, plant.sp). 
## To parse by elev.class2: niche_analysis(net, bb_traits, plant.sp)
## To parse by  elev.class2, period, and pollen: niche_analysis(net, bb_traits, plant.sp, period, pollen)
## You get the idea. You should anyway -- you wrote it. https://tidyeval.tidyverse.org/multiple.html
niche_analysis <- function(x, y, criterion, ...) {

@@

  x %>%
    filter(caste != "male") %>%
    #filter(!bb.sp %in% c("psit", "gers", "humi")) %>% # omit parasitic species, gers because it's a specialist, humi because it's so rare
    filter(!bb.sp %in% c("gers", "humi")) %>% # gers because it's a specialist, humi because it's so rare
    #filter(bb.sp %in% c("bss", "pasc", "prat", "hort", "soro", "wurf")) %>% # focal species
    group_by(site, date, bb.sp, !!criterion, ...) %>% # pooling all sites and years
    summarize(freq = n()) %>% # get interaction frequency for each BB-FL pair
    group_by(site, date, bb.sp) %>%
    mutate(prop = freq/sum(freq)) %>%
    group_by(site, date, ...) %>%
    complete(bb.sp, !!criterion, fill = list(prop = 0)) %>% # fill in zeros for unvisited plants
    group_by(..., bb.sp, !!criterion) %>%
    summarize(prop = mean(prop)) %>%
    #dplyr::select(-freq) %>% # drop freq variable
    group_by(...) %>%
    nest()  %>% # nest into list-column
    mutate(comm1 = map(data, # spread into the kind of array vegan likes
                       function(x) pivot_wider(x, names_from = !!criterion, values_from = prop) %>%
                         replace(is.na(.), 0)
                       ), 
           comm2 = map(comm1, # column to rowname
                       function(x) column_to_rownames(x, var = "bb.sp")
                       ),
           pcoa = map(comm2, # call PCoA
                      function(x) capscale(x ~ 1, distance = "horn")
                      ),
           traits = map(comm1, # join BB traits
                        function(x) x %>% 
                          left_join(y) %>% # y is the trait table, an argument in the main function call
                          column_to_rownames(var = "bb.sp") %>% 
                          select(pbl.w) # pbl.w is the variable I'm interested in
                        ),
           adonis = map2(comm2, traits, # run adonis permuatation test for distance ~ tongue class
                         function(x, y) adonis(x ~ pbl.w, data = y, method = "horn")
                         ),
           pcoa.fort = map(pcoa, pcoa_fort),
           pcoa.plot = map(pcoa.fort, pcoa_plot),
           adonis.r2 = map(adonis, # extract adonis r2
                           function(x) x$aov.tab$R2[[1]]
                           ),
           adonis.p = map(adonis, # extract adonis p-value
                          function(x) x$aov.tab$'Pr(>F)'[[1]]
                          ),
           ordisurf = map2(pcoa, traits, function(x, y) ordisurf(x ~ pbl.w, data = y, k = 8)),
           #ordisurf = map2(pcoa, traits, function(x, y) ordisurf(x ~ pbl.w, data = y, k = 5)),
           ordisurf.dev_exp = map(ordisurf, function(x) summary(x)$dev.expl),
           ordisurf.p = map(ordisurf, function(x) summary(x)$s.pv),
           ordisurf.plot = map2(ordisurf, pcoa.fort, surfplot),
           var.exp.MDS1 = map(pcoa, # extract variance explained by MDS1
                      function(x) x$CA$eig[[1]] / sum(x$CA$eig)
                      ), 
           var.exp.MDS2 = map(pcoa, # extract variance explained by MDS2
                      function(x) x$CA$eig[[2]] / sum(x$CA$eig)
                      )) %>%
    unnest(cols = c(ordisurf.dev_exp, ordisurf.p, adonis.r2, 
                    adonis.p, var.exp.MDS1, var.exp.MDS2)) %>% # these are lists of length = 1, so unnesting them simply displays the value
    mutate(var.exp.MDS1_MDS2 = var.exp.MDS1 + var.exp.MDS2) %>%
    select(..., pcoa, pcoa.plot, var.exp.MDS1_MDS2, var.exp.MDS1, var.exp.MDS2, 
            ordisurf.dev_exp, ordisurf.p, adonis.r2, adonis.p,
            ordisurf, ordisurf.plot, adonis, comm2, traits, pcoa.fort)
}

@@

  a <- x %>%
    filter(caste != "male") %>%
    filter(bb.sp %in% c("bss", "pasc", "prat", "hort", "soro", "wurf")) %>% # focal species
    left_join(y) %>%
    #group_by(elev.class2) %>%
    group_by(site) %>%
    mutate(period = cut_interval(dayofyear, 3, labels = c("early",  "mid", "late"))) %>%
    group_by(site, period, pbl.fac, !!criterion) %>% # group by site, date, bee species, plant species
    summarize(freq = n()) %>% # calculate interaction frequency per species pair within each site
    unite(webID, c(site, period), sep = "_") %>%
    ungroup() %>%
    dplyr::select(higher = pbl.fac, lower = !!criterion, webID, freq) %>% # rename columns to match bipartite's expectations
    data.frame() %>% # convert to data frame
    frame2webs() %>% # convert to to bipartite web
    map(specieslevel, level = "higher", index = indices) %>%
    map(rownames_to_column) %>%
    map(as_tibble) %>%
    bind_rows(.id = "webID") %>% # Collapse list into big data frame
    rename(pbl.fac = rowname) %>%
    separate(webID, c("site", "period"), sep =  "_") %>%
    left_join(z) %>%
    filter(pbl.fac %in% c("long", "short")) %>% # for some reason, a few rows have a "1" for pbl.fac, and I don't know where this comes from; this gets rid of it, but I would still like to know why
    mutate(site = factor(site),
           period = factor(period, levels = c("early", "mid", "late")))

  b <- x %>%
    filter(caste != "male") %>%
    filter(bb.sp %in% c("bss", "pasc", "prat", "hort", "soro", "wurf")) %>% # focal species
    #group_by(elev.class2) %>%
    group_by(site) %>%
    mutate(period = cut_interval(dayofyear, 3, labels = c("early",  "mid", "late"))) %>%
    left_join(bb_traits) %>%
    group_by(site, period, pbl.fac) %>% # group by site, date, bee species, plant species
    summarize(abund = n()) %>%
    group_by(site, period) %>%
    mutate(prop = abund/sum(abund))

@@

  a <- x %>%
    filter(caste != "male") %>%
    filter(bb.sp %in% c("bss", "pasc", "prat", "hort", "soro", "wurf")) %>% # focal species
    left_join(y) %>%
    # group_by(elev.class2) %>%
    # mutate(period = cut_interval(dayofyear, 3, labels = c("early",  "mid", "late"))) %>%
    #group_by(site, period, pbl.fac, !!criterion) %>% # group by site, date, bee species, plant species
    group_by(site, pbl.fac, !!criterion) %>% # group by site, date, bee species, plant species
    summarize(freq = n()) %>% # calculate interaction frequency per species pair within each site
    #unite(webID, c(site, period), sep = "_") %>%
    ungroup() %>%
    #dplyr::select(higher = pbl.fac, lower = !!criterion, webID, freq) %>% # rename columns to match bipartite's expectations
    dplyr::select(higher = pbl.fac, lower = !!criterion, webID = site, freq) %>% # rename columns to match bipartite's expectations
    data.frame() %>% # convert to data frame
    frame2webs() %>% # convert to to bipartite web
    map(specieslevel, level = "higher", index = indices) %>%
    map(rownames_to_column) %>%
    map(as_tibble) %>%
    bind_rows(.id = "webID") %>% # Collapse list into big data frame
    #rename(pbl.fac = rowname) %>%
    rename(pbl.fac = rowname,
           site = webID) %>%
    #separate(webID, c("site", "period"), sep =  "_") %>%
    left_join(z) %>%
    filter(pbl.fac %in% c("long", "short")) %>% # for some reason, a few rows have a "1" for pbl.fac, and I don't know where this comes from; this gets rid of it, but I would still like to know why
    # mutate(site = factor(site),
    #        period = factor(period, levels = c("early", "mid", "late")))
    mutate(site = factor(site))

  b <- x %>%
    filter(caste != "male") %>%
    filter(bb.sp %in% c("bss", "pasc", "prat", "hort", "soro", "wurf")) %>% # focal species
    # group_by(elev.class2) %>%
    # mutate(period = cut_interval(dayofyear, 3, labels = c("early",  "mid", "late"))) %>%
    left_join(bb_traits) %>%
   # group_by(site, period, pbl.fac) %>% # group by site, date, bee species, plant species
    group_by(site, pbl.fac) %>% # group by site, date, bee species, plant species
    summarize(abund = n()) %>%
    #group_by(site, period) %>%
    group_by(site) %>%
    mutate(prop = abund/sum(abund))

@@

## 1.1 Ordination by species with post-hoc fitting of tongue length  
### Script
```{r message=FALSE, warning=FALSE, echo = FALSE}
# By plant.sp
niche.tax <- niche_analysis(net, bb_traits, criterion = plant.sp.abb)
niche.tax.plot <- niche.tax$ordisurf.plot[[1]]

# By ktype
niche.morph <- niche_analysis(net, bb_traits, criterion = k.type.s)
niche.morph.plot <- niche.morph$ordisurf.plot[[1]]

# By color
niche.color <- niche_analysis(net, bb_traits, criterion = color)
niche.color.plot <- niche.color$pcoa.plot[[1]]

## Taxonomic and morphological together
pdf("../analyses/output/niche_pcoa.pdf", height = 8.5, width = 11)
(niche.tax.plot + ggtitle("Taxonomic") | niche.morph.plot + ggtitle("Morphological")) + plot_layout(guides = 'keep') 
dev.off()

@@

## Extract and name plots
niche_high.tax.plot <- filter(niche_x_elev.tax, elev.class2 == "high")$ordisurf.plot[[1]] + ggtitle("high/Tax")
niche_mid.tax.plot <- filter(niche_x_elev.tax, elev.class2 == "mid")$ordisurf.plot[[1]] + ggtitle("mid/Tax")
niche_low.tax.plot <- filter(niche_x_elev.tax, elev.class2 == "low")$ordisurf.plot[[1]] + ggtitle("low/Tax")

# Morphological
niche_x_elev.morph <- niche_analysis(net, bb_traits, criterion = k.type.ss, elev.class2)

## Extract and name plots
niche_high.morph.plot <- filter(niche_x_elev.morph, elev.class2 == "high")$ordisurf.plot[[1]] + ggtitle("high/morph")
niche_mid.morph.plot <- filter(niche_x_elev.morph, elev.class2 == "mid")$ordisurf.plot[[1]] + ggtitle("mid/morph")
niche_low.morph.plot <- filter(niche_x_elev.morph, elev.class2 == "low")$ordisurf.plot[[1]] + ggtitle("low/morph")

# Color
niche_x_elev.color <- niche_analysis(net, bb_traits, criterion = color, elev.class2)

## Extract and name plots
niche_high.color.plot <- filter(niche_x_elev.color, elev.class2 == "high")$pcoa.plot[[1]] + ggtitle("high/color")
niche_mid.color.plot <- filter(niche_x_elev.color, elev.class2 == "mid")$pcoa.plot[[1]] + ggtitle("mid/color")
niche_low.color.plot <- filter(niche_x_elev.color, elev.class2 == "low")$pcoa.plot[[1]] + ggtitle("low/color")

## Display plots on grid
pdf("../analyses/output/niche_x_elev_pcoa.pdf", height = 8.5, width = 11)
(niche_high.tax.plot | niche_high.morph.plot) /
(niche_mid.tax.plot | niche_mid.morph.plot) /
(niche_low.tax.plot | niche_low.morph.plot) + plot_layout(guides = 'keep') 
dev.off()
```

@@

## Extract and name plots
niche_high_early.tax.plot <- filter(niche_x_elevperiod.tax, elev.class2 == "high" & period == "early")$ordisurf.plot[[1]] 
# niche_high_mid1.tax.plot <- filter(niche_x_elevperiod.tax, elev.class2 == "high" & period == "mid1")$ordisurf.plot[[1]] 
# niche_high_mid2.tax.plot <- filter(niche_x_elevperiod.tax, elev.class2 == "high" & period == "mid2")$ordisurf.plot[[1]]
niche_high_mid.tax.plot <- filter(niche_x_elevperiod.tax, elev.class2 == "high" & period == "mid")$ordisurf.plot[[1]]
niche_high_late.tax.plot <- filter(niche_x_elevperiod.tax, elev.class2 == "high" & period == "late")$ordisurf.plot[[1]]

niche_mid_early.tax.plot <- filter(niche_x_elevperiod.tax, elev.class2 == "mid" & period == "early")$ordisurf.plot[[1]]
# niche_mid_mid1.tax.plot <- filter(niche_x_elevperiod.tax, elev.class2 == "mid" & period == "mid1")$ordisurf.plot[[1]] 
# niche_mid_mid2.tax.plot <- filter(niche_x_elevperiod.tax, elev.class2 == "mid" & period == "mid2")$ordisurf.plot[[1]]
niche_mid_mid.tax.plot <- filter(niche_x_elevperiod.tax, elev.class2 == "mid" & period == "mid")$ordisurf.plot[[1]]
niche_mid_late.tax.plot <- filter(niche_x_elevperiod.tax, elev.class2 == "mid" & period == "late")$ordisurf.plot[[1]]

niche_low_early.tax.plot <- filter(niche_x_elevperiod.tax, elev.class2 == "low" & period == "early")$ordisurf.plot[[1]]
# niche_low_mid1.tax.plot <- filter(niche_x_elevperiod.tax, elev.class2 == "low" & period == "mid1")$ordisurf.plot[[1]]
# niche_low_mid2.tax.plot <- filter(niche_x_elevperiod.tax, elev.class2 == "low" & period == "mid2")$ordisurf.plot[[1]]
niche_low_mid.tax.plot <- filter(niche_x_elevperiod.tax, elev.class2 == "low" & period == "mid")$ordisurf.plot[[1]]
niche_low_late.tax.plot <- filter(niche_x_elevperiod.tax, elev.class2 == "low" & period == "late")$ordisurf.plot[[1]]

@@

## Extract and name plots
niche_high_early.morph.plot <- filter(niche_x_elevperiod.morph, elev.class2 == "high" & period == "early")$ordisurf.plot[[1]]
niche_high_mid1.morph.plot <- filter(niche_x_elevperiod.morph, elev.class2 == "high" & period == "mid1")$ordisurf.plot[[1]] 
niche_high_mid2.morph.plot <- filter(niche_x_elevperiod.morph, elev.class2 == "high" & period == "mid2")$ordisurf.plot[[1]] 
niche_high_late.morph.plot <- filter(niche_x_elevperiod.morph, elev.class2 == "high" & period == "late")$ordisurf.plot[[1]]

niche_mid_early.morph.plot <- filter(niche_x_elevperiod.morph, elev.class2 == "mid" & period == "early")$ordisurf.plot[[1]]
niche_mid_mid1.morph.plot <- filter(niche_x_elevperiod.morph, elev.class2 == "mid" & period == "mid1")$ordisurf.plot[[1]]
niche_mid_mid2.morph.plot <- filter(niche_x_elevperiod.morph, elev.class2 == "mid" & period == "mid2")$ordisurf.plot[[1]] 
niche_mid_late.morph.plot <- filter(niche_x_elevperiod.morph, elev.class2 == "mid" & period == "late")$ordisurf.plot[[1]]
